\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Update fig caption

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. \textbf{Figure needed} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. The full target orchestration places all onsets at the beginning of the orchestration, since it is unable to differentiate between different sources, it cannot place the different orchestrations at the appropriate offsets. However, the separated orchestrations are able to correctly place the onsets of the sub-target orchestrations so far as the method has correctly separated out the sources. In the ground truth orchestration, the sources are offset by the same amount as they are in the creation of the target, leading to the ground truth having each source orchestration beginning at the correct time.

>>>>

		\begin{figure}[t]
		\centering
			\includegraphics[width=\columnwidth]{figures/orch.jpg}
			\caption{Example waveforms showing onsets of the four sources in the target, and possible onsets in the full, separated, and ground truth orchestrations. In this example, the separation method could not distinguish between sources 2 and 3 and identified them as a single sub-target. Therefore, the separated orchestration has only 3 onsets, one of them being an orchestration that combines sources 2 and 3. Note that this is a simplified representation, in the actual targets sources overlap in time and are not as discrete as this diagram shows.}\label{fig:orchestrations}
		\end{figure}

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure \ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. The full target orchestration places all onsets at the beginning of the orchestration, since it is unable to differentiate between different sources, it cannot place the different orchestrations at the appropriate offsets. However, the separated orchestrations are able to correctly place the onsets of the sub-target orchestrations so far as the method has correctly separated out the sources. In the ground truth orchestration, the sources are offset by the same amount as they are in the creation of the target, leading to the ground truth having each source orchestration beginning at the correct time.
